MINOS Handover Plots

### 2023-10-05 minos/validation/handovers.Rmd
Changed matdep proxy to a 3 level ordinal and fit a CLM model to it. Handovers look good

```{r}
#  nutriton quality line/boxplots.
handover_boxplots(raw.dat, base.dat, 'nutrition_quality')
handover_lineplots(raw.dat, base.dat, 'nutrition_quality')
```

@@

```{r}
# raw.nut <- raw.dat %>%
#   select(pidp, age, time, nutrition_quality)
# base.nut <- base.dat %>%
#   select(pidp, age, time, nutrition_quality)
# 
# nut.spag <- rbind(raw.nut, base.nut)
# 
# spaghetti_plot(nut.spag, 'nutrition_quality',
#                save = shall.we.save,
#                save.path = save.path)
# 
# 
# density_ridges(nut.spag, "nutrition_quality", 
#                save = T, 
#                save.path = save.path)
# 
# rm(raw.nut, base.nut, nut.spag)
```

@@

```{r}
handover_boxplots(raw.dat, base.dat, 'matdep')
handover_lineplots(raw.dat, base.dat, 'matdep')
```

>>>>

```{r}
#  nutriton quality line/boxplots.
handover_boxplots(raw.dat, base.dat, 'nutrition_quality')
handover_lineplots(raw.dat, base.dat, 'nutrition_quality')

test.pidps <- raw.dat %>%
  select(pidp)

test.base <- base.dat %>%
  filter(pidp %in% test.pidps$pidp)

handover_boxplots(raw.dat, test.base, 'nutrition_quality')
handover_lineplots(raw.dat, test.base, 'nutrition_quality')
```

@@

```{r}
raw.nut <- raw.dat %>%
  select(pidp, age, time, nutrition_quality)
base.nut <- base.dat %>%
  select(pidp, age, time, nutrition_quality)

nut.spag <- rbind(raw.nut, base.nut)

spaghetti_plot(nut.spag, 'nutrition_quality',
               save = shall.we.save,
               save.path = save.path)

density_ridges(nut.spag, "nutrition_quality",
               save = T,
               save.path = save.path)

rm(raw.nut, base.nut, nut.spag)
```

## Tobacco

```{r}
#  nutriton quality line/boxplots.
handover_boxplots(raw.dat, base.dat, 'ncigs')
handover_lineplots(raw.dat, base.dat, 'ncigs')

test.pidps <- raw.dat %>%
  select(pidp)

test.base <- base.dat %>%
  filter(pidp %in% test.pidps$pidp)

handover_boxplots(raw.dat, test.base, 'ncigs')
handover_lineplots(raw.dat, test.base, 'ncigs')
```

```{r}
raw.nut <- raw.dat %>%
  select(pidp, age, time, ncigs)
base.nut <- base.dat %>%
  select(pidp, age, time, ncigs)

nut.spag <- rbind(raw.nut, base.nut)

spaghetti_plot(nut.spag, 'ncigs',
               save = shall.we.save,
               save.path = save.path)

density_ridges(nut.spag, "ncigs",
               save = FALSE,
               save.path = save.path)

rm(raw.nut, base.nut, nut.spag)
```

@@

```{r}
#handover_boxplots(raw.dat, base.dat, 'matdep')
#handover_lineplots(raw.dat, base.dat, 'matdep')
handover_ordinal(raw.dat, base.dat, var = 'matdep', save = shall.we.save)
```

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, matdep) %>%
#   filter(!matdep %in% miss.values)
# base.s <- base.dat %>%
#   select(pidp, age, time, matdep) %>%
#   filter(!matdep %in% miss.values)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'matdep',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```
